Stop Data Analysis

### 2016-08-09 eda/PaperDrafts/Stop_Data_Analysis.Rmd

```{r, echo=FALSE, eval=FALSE}
stop_race_total_table <- stop_by %>%
    group_by(Race) %>%
    summarise(totaLCount = n())
stop_race_agerange_table <- stop_by %>%
    group_by(Race, AgeRange) %>%
    summarise(count = n())
stop_race_table <- left_join(stop_race_agerange_table, stop_race_total_table, by = "Race")
stop_race_table <- stop_race_table %>%
    mutate(percentage = count/totaLCount) %>%
    select(-count)
stop_race_table <- stop_race_table %>%
    spread(key = AgeRange, value = percentage)
stop_race_table
```

@@

```{r, eval=FALSE, echo=FALSE}
stop_day_total_table <- stop_by %>%
    group_by(Day) %>%
    summarise(totaLCount = n())
stop_day_race_table <- stop_by %>%
    group_by(Day, Race) %>%
    summarise(count = n())
stop_day_table <- left_join(stop_day_race_table, stop_day_total_table, by = "Day")
stop_day_table <- stop_day_table %>%
    spread(key = Race, value = count)
stop_day_table
```
####Picture: count of person recorded in each day in a week
Day   | Count | A    | B    | H    | O    | W
----  |------ |------|------|------|------|------
1     | 1692  | 116  | 653  | 221  | 159  | 543
2     | 1665  | 149  | 543  | 182  | 166  | 625
3     | 2344  | 189  | 645  | 231  | 236  | 1043
4     | 2287  | 206  | 616  | 251  | 244  | 970
5     | 1941  | 152  | 592  | 223  | 168  | 806
6     | 2231  | 186  | 764  | 268  | 203  | 810
7     | 2131  | 143  | 823  | 300  | 208  | 657

@@

### Analysis of incidents of each hour in a day
#### Picture: count of person recorded in each hour in a day
```{r, echo=FALSE}
stop_time <- stop_by %>%
  ggvis(x = ~Hour, fill := "lightpink") %>%
  layer_histograms(width = input_slider(1, 12, value = 1, step = 2, label = "width"))
stop_time
```
Note: you can change the value of the input slider to see the number of incidents happened in specific time span of the day.
```{r, eval = FALSE, echo=FALSE}
stop_hour <- stop_by %>%
  group_by(Hour) %>%
  summarise(count = n())
stop_hour
```

@@

### Analysis of prefence of Berkeley Police Department arresting people
#### Picture: Probability of arrested by BPD of a specific race for a specific reason
```{r,echo=FALSE}
stop_by_reason_race <- stop_by %>%
  group_by(Race, Reason) %>%
  summarise(totalCount = n())
stop_by_arrest <- stop_by %>%
  filter(Enforcement == "A") %>%
  group_by(Race, Reason) %>%
  summarise(arrestCount = n())
stop_by_percentage_race <- left_join(stop_by_reason_race, stop_by_arrest, by = c("Race", "Reason"))
stop_by_percentage_race <- stop_by_percentage_race %>%
  mutate(percentage = arrestCount / totalCount)
stop_arrest <- ggplot(stop_by_percentage_race, aes(x = Race, fill = Race)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest
```

@@

stop_arrest_age <- ggplot(stop_by_percentage_age, aes(x = AgeRange, fill = AgeRange)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest_age
```

@@

stop_arrest_gender <- ggplot(stop_by_percentage_gender, aes(x = Gender, fill = Gender)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_wrap(~Reason)
stop_arrest_gender
```

>>>>

```{r, echo=FALSE}
stop_race_total_table <- stop_by %>%
    group_by(Race) %>%
    summarise(totaLCount = n())
stop_race_agerange_table <- stop_by %>%
    group_by(Race, AgeRange) %>%
    summarise(count = n())
stop_race_table <- left_join(stop_race_agerange_table, stop_race_total_table, by = "Race")
stop_race_table <- stop_race_table %>%
    mutate(percentage = count/totaLCount) %>%
    select(-count)
stop_race_table <- stop_race_table %>%
    spread(key = AgeRange, value = percentage)
stop_race_table
```

@@

```{r, echo=FALSE}
stop_day_total_table <- stop_by %>%
    group_by(Day) %>%
    summarise(totaLCount = n())
stop_day_race_table <- stop_by %>%
    group_by(Day, Race) %>%
    summarise(count = n())
stop_day_table <- left_join(stop_day_race_table, stop_day_total_table, by = "Day")
stop_day_table <- stop_day_table %>%
    spread(key = Race, value = count)
stop_day_table
```
####Picture: count of person recorded in each day in a week
Day   | Count | A    | B    | H    | O    | W
----  |------ |------|------|------|------|------
1     | 1692  | 116  | 653  | 221  | 159  | 543
2     | 1665  | 149  | 543  | 182  | 166  | 625
3     | 2344  | 189  | 645  | 231  | 236  | 1043
4     | 2287  | 206  | 616  | 251  | 244  | 970
5     | 1941  | 152  | 592  | 223  | 168  | 806
6     | 2231  | 186  | 764  | 268  | 203  | 810
7     | 2131  | 143  | 823  | 300  | 208  | 657

@@

### Analysis of incidents of each hour in a day
#### Picture: count of person recorded in each hour in a day
```{r, echo=FALSE}
stop_race <- ggplot(stop_by, aes(x = Hour, fill = CarSearch)) + 
  geom_bar(aes(y = ..count../sum(..count..))) + 
  scale_fill_brewer(palette = "Pastel2") +
  labs(y = "Density")
stop_race
```
Note: you can change the value of the input slider to see the number of incidents happened in specific time span of the day.
```{r, echo=FALSE}
stop_hour <- stop_by %>%
  group_by(Hour) %>%
  summarise(count = n())
stop_hour
```

@@

### Analysis of prefence of Berkeley Police Department arresting people
#### Picture: Probability of arrested by BPD of a specific race for a specific reason
```{r,echo=FALSE, fig.asp=0.5, fig.height=3, fig.width=15}
stop_by_reason_race <- stop_by %>%
  group_by(Race, Reason) %>%
  summarise(totalCount = n())
stop_by_arrest <- stop_by %>%
  filter(Enforcement == "A") %>%
  group_by(Race, Reason) %>%
  summarise(arrestCount = n())
stop_by_percentage_race <- left_join(stop_by_reason_race, stop_by_arrest, by = c("Race", "Reason"))
stop_by_percentage_race <- stop_by_percentage_race %>%
  mutate(percentage = arrestCount / totalCount)
stop_arrest <- ggplot(stop_by_percentage_race, aes(x = Race, fill = Race)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_grid(~Reason)
stop_arrest
```

@@

stop_arrest_age <- ggplot(stop_by_percentage_age, aes(x = AgeRange, fill = AgeRange)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_grid(~Reason)
stop_arrest_age
```

@@

stop_arrest_gender <- ggplot(stop_by_percentage_gender, aes(x = Gender, fill = Gender)) + 
  geom_bar(aes(y = percentage), stat="identity") +
  labs(y = "Density") +
  facet_grid(~Reason)
stop_arrest_gender
```
